The Globular Cluster System of the Auriga Simulations

### 2019-03-24 AurigaGCS.tex
Second paragraph of introduction: two GC subpopulations

\section{Introduction}
Globular clusters (GCs) are old, ubiquitous, bright, and amongst the simplest
stellar configurations in the Universe. They inherit properties from their natal
gas, and the properties of globular cluster systems correlate with those of
(the field stars in) their host galaxies. In theory, this means that GC systems 
are excellent tracers of the formation and evolution of their host galaxies, if 
the formation of the GCs themselves is well-understood.

\todo[inline]{Paragraph: Theories of GC formation}

>>>>

\section{Introduction}
Globular clusters (GC)s are omnipresent, bright, old, and amongst the simplest
stellar configurations in the Universe. Their visbility and ubiquity make it 
possible to obtain integrated GC quantities of galaxies in the Local Group. 
Moreover, GCs inherit characteristics from their natal gas and GC systems show 
correlations with properties of (the field stars in) their host galaxies. For 
example, the mean metallicity of GC systems in early-type galaxies correlates with 
the galactic metallicity (van den Bergh 1975, Brodie \& Huchra 1991) as well as 
with the luminosity and possibly the mass (Larsen 2001; Peng 2006). The old ages
are consistent with formation before, during, or shortly after the initial
collapse of the proto-galaxy. In theory, all of these characteristics make GC
systems excellent tracers of the formation and evolution of their parent galaxies,
if the formation of GCs themselves is well-understood.

Most galaxies host GC systems with a bimodal colour distribution, indicative of
a bimodal metallicity distribution. The Milky Way (MW) GC system (GCS) can be
split up in a metal-rich (red) and metal-poor (blue) subpopulation divided at
[Fe/H]~$=-1$ \citep[e.g.][]{Harris2001}, although slightly different values can
also be found in the literature. The two subpopulations are believed to be
associated to the galactic disk, respectively the stellar halo 
\citep{1985ApJ...293..424Z}. The latter is supported by observed similarities 
between the spatial distribution and chemical signature of the `blue' GCs show 
and stars in the stellar halo \citep{2008A&ARv..15..145H}. Moreover, relative 
age-estimates show an offset of $1.5$~Gyr between both subpopulations 
\citep{2005AJ....130..116D}.

\citet{2006ARA&A..44..193B} review extragalactic GCs and galaxy 
formation, and argue that the observed metal-rich and metal-poor
